Cluster Detection from three-dimensional Lensing Mass Map

### 2021-01-07 doc/paper_ms_method_HSCY1/massmap_sim.tex
add planck2018

The $\Lambda$CDM cosmology used in this paper is from the best-fit result of
the final full-mission Planck observation of the cosmic microwave background
(CMB) with $H_0=67.4 ~\rm{km~s^{-1} Mpc^{-1}}$ $\Omega_M=0.315$,
$\Omega_\Lambda=0.685$ \citep{cmb-Planck2018-Cosmology}.

We sample halos in a two-dimensional redshift-mass plane. The redshift-mass
plane is evenly divided into eight redshift bins and eight mass bins. We
randomly shift the input halo redshifts and halo masses from the bins' centers
by a small amount. The concentration of the NFW halo is set as a function of
the halo's mass ($M_{200}$) and redshift ($z_{h}$) according to
\citet{c-M_Magneticum-Ragagnin2019}
\begin{equation}
c_{h}=6.02\times(\frac{M_{200}}{10^{13} M_{\odot}})^{-0.12}(\frac{1.47}{1.+z_h})^{0.16}.
\end{equation}
The weak-lensing shear fields of these NFW halos are simulated according to
\citet{haloModel-TJ2003-3pt}. The shear distortions are applied to one hundred
realizations of galaxy catalogs with the HSC-like shape measurement error and
photo-$z$ uncertainty.

>>>>

The $\Lambda$CDM cosmology used in this paper is from the best-fit result of
the final full-mission Planck observation of the cosmic microwave background
(CMB) with $H_0=67.4 ~\rm{km~s^{-1} Mpc^{-1}}$ $\Omega_M=0.315$,
$\Omega_\Lambda=0.685$, $\sigma_8=0.811$, $n_s=0.965$
\citep{cmb-Planck2018-Cosmology}.

We sample halos in a two-dimensional redshift-mass plane. The redshift-mass
plane is evenly divided into eight redshift bins and eight mass bins. We
randomly shift the input halo redshifts and halo masses from the bins' centers
by a small amount. The concentration of the NFW halo is set as a function of
the halo's virial mass ($M_{200}$) and redshift ($z_{h}$) according to
\citet{c-M_Magneticum-Ragagnin2019}
\begin{equation}
c_{h}=6.02\times\left(\frac{M_{200}}{10^{13} M_{\odot}}\right)^{-0.12}
\left(\frac{1.47}{1.+z_h}\right)^{0.16}.
\end{equation}
The weak-lensing shear fields of these NFW halos are simulated according to
\citet{haloModel-TJ2003-3pt}. The shear distortions are applied to one hundred
realizations of galaxy catalogs with the HSC-like shape measurement error and
photo-$z$ uncertainty.
